Comparison among doublet predictions on benchmarking datasets

### 2024-07-02 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd
Apply suggestions from code review
Co-authored-by: Ally Hawkins <54039191+allyhawkins@users.noreply.github.com>

Next, well explore the consensus of doublet predictions across methods. 
To this end, we'll create some new columns for each dataset:

@@

      pc_color_columns <- c("scDblFinder prediction" = "scdbl_prediction",
                            "scublet prediction" = "scrublet_prediction",
                            "cxds prediction" = "cxds_prediction",
                            "Ground truth" = "ground_truth", 
                            "Consensus call" = "consensus_call")

>>>>

Next, we will explore the consensus of doublet predictions across methods. 
To this end, we'll create some new columns for each dataset:

@@

      pc_color_columns <- c("scDblFinder prediction" = "scdbl_prediction",
                            "scrublet prediction" = "scrublet_prediction",
                            "cxds prediction" = "cxds_prediction",
                            "Ground truth" = "ground_truth", 
                            "Consensus call" = "consensus_call")
